# Communicable, Maternal, Neonatal, and Nutritional Disease Burden (CMNN)

```{r}
# Load necessary packages
pacman::p_load(tidyverse, knitr, here)

# Import the communicable diseases data
data_cmnn <- read_csv(here("data/burden-of-disease-cmnn.csv"))
```

```{r}
# Filter the dataset to include only the three countries chosen by your group.
data_cmnn_mini <- data_cmnn %>% 
                  filter(Code %in% c("CAN", "DEU", "MEX")) %>% select (-Code)
```

## Table of Estimates for CMNN Burden Over Time

```{r}
# Here render a table for the DALY burden over time for the three countries.
# You should pivot the data wider to show each country in a separate column.
data_cmnn_wide <- data_cmnn_mini %>%  pivot_wider(names_from = "Entity", values_from = "DALYs (Disability-Adjusted Life Years) - Communicable, maternal, neonatal, and nutritional diseases - Sex: Both - Age: Age-standardized (Rate)") 

# Use kable() from the knitr package to render the table.
  kable(data_cmnn_wide)
```

## Plot Showing Trends in CMNN Burden Over Time

```{r include = F}
# Here, plot a line graph showing the trend of DALY burden for the chosen countries over time. You can use ggplot2 to create this plot. Each country's line should be a different color.
# NOTE: Use your long 'mini' data frame for plotting, not the wide data used for the table.
names(data_cmnn_mini)[3] <- "DALYs_cmnn"
plot_cmnn_mini <- ggplot(data_cmnn_mini, aes(x=Year, y= DALYs_cmnn, group=Entity)) + 
                  geom_line(aes(color=Entity)) +
                  geom_point(aes(color=Entity)) +
                  theme_bw() +
                  ylab("DALYs (Disability-Adjusted Life Years) - Communicable,\nmaternal, neonatal, and nutritional diseases -\nSex: Both - Age: Age-standardized (Rate)")
```
```{r}
plot_cmnn_mini
```

## Summary of CMNN Burden Findings

Canada and Germany exhibit similar patterns, both with a mild decreasing trend. Mexico on the other hand, shows a much steeper decrease. However, on 2015 the gap between Mexico and Canada is still remarkable. Of course, this is not population-size adjusted.


## Attribution

This section was completed by *qwertz19*.

The link to the group's GitHub repository is https://github.com/pscprz/rmc_week_02_workshop
