# Overall Disease Burden

```{r}
# Load necessary packages
pacman::p_load(tidyverse, knitr, here)

# Import the overall disease data
data_overall <- read_csv(here("data/burden-of-disease-all-causes.csv"))
```

```{r}
# Filter the dataset to include only the three countries chosen by your group.
data_overall_mini <- data_overall %>% 
                  filter(Code %in% c("CAN", "DEU", "MEX")) %>% 
                  select (-Code)
```

## Table of Estimates for Overall Disease Burden Over Time

```{r}
# Here render a table for the DALY burden over time for the three countries.
# You should pivot the data wider to show each country in a separate column.
data_overall_wide <- data_overall_mini %>%  
  pivot_wider(names_from = "Entity", values_from = "DALYs (Disability-Adjusted Life Years) - All causes - Sex: Both - Age: Age-standardized (Rate)")

# Use kable() from the knitr package to render the table.
kable(data_overall_wide)
```

## Plot Showing Trends in Overall Disease Burden Over Time

```{r include = F}
# Here, plot a line graph showing the trend of DALY burden for the chosen countries over time. You can use ggplot2 to create this plot. Each country's line should be a different color.
# NOTE: Use your long 'mini' data frame for plotting, not the wide data used for the table.
names(data_overall_mini)[3] <- "DALYs_all"
plot_overall_mini <- ggplot(data_overall_mini, aes(x=Year, y= DALYs_all, group=Entity)) + 
                    geom_line(aes(color=Entity)) +
                    geom_point(aes(color=Entity)) +
                    theme_bw() +
                    ylab("DALYs (Disability-Adjusted Life Years) - All causes -\nSex: Both - Age: Age-standardized (Rate)")
```
```{r}
plot_overall_mini
```

## Summary of Overall Disease Burden Findings


All three countries exhibit a decreasing trend over time. Nevertheless, Mexico surpasses both Germany and Canada by far. Also there are slight fluctuation from 2005. 

Canada registered the lowest values of the three countries over time, being followed by Germany, specially from 2010 onwards.  

## Attribution

This section was completed by *qwertz19*.

The link to the group's GitHub repository is https://github.com/pscprz/rmc_week_02_workshop
